### 2008-12-01 doc/sec/Sec_paper.tex
Abstract about sec paper

Abstract-{}-

@@

@@

\liststyleLi
\begin{enumerate}
\item {\centering
Introduction
\par}

\bigskip
\end{enumerate}

@@

@@

3. Cross-domain authentication and Single Sign-On

@@

\ \ Community based authentication: Utilizing Shibboleth IdP

@@

\ \ Short-lived certificate service

@@

\ \ Certificate delegation service

@@

\ \ From transport level security to message level security: X.509 Token
and SAML Token

@@

\ \ Delegation between WS-Security tokens

@@

4. Standardized Attribute-based authorization

@@

@@

>>>>

{\centering
Abstract
\par}

\ In order to make the access to Grids as simple as possible, security
including authentication and authorization is one of the most important
challenges in production Grids, especially when the Grid applications
are across multiple administration domains as well as across
heterogeneous Grid middlewares, such as some widely scaled eScience
applications which needs to coordinate resources sharing among
collection of autonomous institutions with different Grid middlewares
running on these resources. In this paper, we describe the security
implementation and consideration in new version of Advanced Resource
Connector (ARC) middleware, where the above issues have been exploited.
The main goal of ARC implementation in terms of security is to let the
middleware be capable to \ interoperate with other Grid middlewares by
leveraging standard specifications. The key aspect of the work we have
done is to enhance the current proxy certificate based delegation and
authentication by utilizing the Security Assertion Markup Languages
(\textit{SAML}) single sign-on (SSO) profile, WS-Security in order to
achieve cross-domain authentication, as well as to enhance the
Attribute Certificate (AC) based authorization by utilizing the SAML
\ attribute query profile in order to achieve standardized
attribute-based authorization. \

@@

\liststyleLi
\begin{enumerate}
\item[] {\centering
1. Introduction
\par}
\end{enumerate}

@@

@@

HED contains a framework for implementing and enforcing authentication
and authorization. Each Message Chain Component (MCC) or service has a
common interface for implementing various authentication and
authorization functionality. This functionality is implemented by using
pluggable and configurable components (plug-ins) called
\textit{SecHandler}. The \textit{SecHandler} components are C++ classes
and provide method for processing messages traveling through Message
Chains of the HED. Each MCC or Service \ usually implement two queues
of SecHandlers -- one for incoming messages and one for outgoing called
{\textquotedblleft}incoming{\textquotedblright} and
{\textquotedblleft}outgoing{\textquotedblright} respectively. All
\textit{SecHandler} components attached to the queue are executed
sequentially. If any of them fails, message processing fails as well.
In figure 1, the {\textquotedblleft}AuthZ{\textquotedblright} and
{\textquotedblleft}AuthN{\textquotedblright} sub-module inside MCCs and
Services are examples of \textit{SecHandler}.

{\centering
3. Cross-domain authentication and Single Sign-On
\par}

@@

\ \ 3.1 Community based authentication: Utilizing Shibboleth IdP

@@

\ \ 3.2 Short-lived certificate service

@@

\ \ 3.3 Certificate delegation service

@@

\ \ 3.4 From transport level security to message level security: X.509
Token and SAML Token

@@

@@

\ \ 3.5 Delegation between WS-Security tokens

@@

{\centering
4. Standardized Attribute-based authorization 
\par}

4.1 SAML Attribute Query profile

4.2 Client to VOMS Attribute authority Service

4.3 Attribute parsing and Policy decision point

@@

{\centering
5. Related work
\par}

VOMS AA Service

Shibboleth

GridShib

gLite Delegation Service?

SWITCH SLCS Service

{\centering
6. Conclusion and Future work
\par}

@@

Reference:
